Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-12 bbbq_article.tex
First self-review

Table \ref{tab:elution} shows the percentage of epitopes derived from a TMH
found in the two elution studies, for the two different kind of topology
prediction tools. Whatever the tool or MHC class, at least 100 epitopes

@@

Figure \ref{fig:1} shows the percentages of MHC-I epitopes overlapping 
with TMHs for our human, viral and bacterial proteome,
when using EpitopePrediction to predict epitopes.
See the supplementary materials (table \ref{tab:tmh_binders_mhc1}) 
for the TMH and epitope counts.

@@

\paragraph{General pattern in epitope presentation}

@@

\paragraph{Interesting haplotype for SARS-CoV-2}

@@

\paragraph{False positives}

@@

\paragraph{Removal of selenoproteins}

@@

\paragraph{Topology prediction of TRDD1}

@@

\paragraph{Bacteria have a different cell membrane}

@@

\paragraph{synonymous mutations}

@@

\paragraph{False positives in SNPs}

@@

\paragraph{Low number of SNPs}

@@

\paragraph{Selection of SNPs}

@@

\subsection{Notes and/or to be removed}

We concluded that the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its bacterial pathogen.
Because a bacterium does not infect a cell, thus its peptides
will not be presented by MHC-I, this result is [unexpected/expected]

We aimed our evolutionary experiment at TMHs, because these can
be predicted well from a protein structure,
are common structures and are present in all pathogens. 
We could have done the same experiment on beta-turn,
as also these can be predicted well (\cite{petersen2010netturnp}),
are common structures and are present in all pathogens.

The human immune system and human pathogen are in an evolutionary
arms race: our immune systems is selected for the detection
of pathogens, whereas pathogens are selected to avoid detection.
From a pathogen's point of view, however, this struggle 
is of only minor importance:
in seasonal influenza, for example, the selection pressure
exerted by the immune system was only limited (\cite{han2019individual}).

@@

\paragraph{TMH prediction software}

@@

\paragraph{IC50 prediction software}

@@

\paragraph{Definition of what a binder is}

@@

\paragraph{Unclear handing of sequences with U}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Uniprot IDs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Table \ref{tab:uniprot_ids} shows an overview of the Uniprot IDs
for the reference proteomes used. Note that for Homo sapiens,
we did not use the full reference proteome, but a representative
and smaller reference proteome instead.

% tab:uniprot_ids
\input{create_table_reference_proteomes/uniprot_ids.latex}

@@

Per target proteome (i.e. human, SARS-CoV-2, Mycobacterium tuberculosis),
we collected all 9-mers (for MHC-I) and 14-mers (for MHC-II),
after removing the selenoproteins and proteins that are shorter
than the epitope length.
From these epitopes, per MHC haplotype,
we predicted the IC50 (in nM) using \verb;epitope-prediction; (for MHC-I)
and MHCnuggets (for MHC-II). 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC
for MHC-I (see \ref{tab:ic50_binders_mhc1}) and 
MHC-II (see \ref{tab:ic50_binders_mhc2}).

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_snps_per_gene_name_ncbi.png}
  \caption{
    Total number of SNPs per gene name.
  }
  \label{fig:snps_per_gene_name_ncbi}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{ncbi_peregrine_results/fig_snps_per_gene_name_processed.png}
  \caption{
    Number of SNPs per gene processed.
  }
  \label{fig:snps_per_gene_name_processed}
\end{figure}

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{snp_workflow.png}
  \caption{
    Workflow to determine the evolutionary conservation of TMHs
    using human SNPs.
  }
  \label{fig:snp_workflow}
\end{figure}

>>>>

Table \ref{tab:elution} shows the percentage of epitopes derived from a TMH
found in the two elution studies, for the two different kind of topology
prediction tools. Whatever the tool or MHC class, at least 100 epitopes
can be uniquely map to human representative reference proteome.

@@

Figure \ref{fig:1} shows the percentages of MHC-I epitopes overlapping 
with TMHs for our human, viral and bacterial proteome.
See the supplementary materials (table \ref{tab:tmh_binders_mhc1}) 
for the exact TMH and epitope counts.

@@

% \paragraph{General pattern in epitope presentation}

@@

% \paragraph{Interesting haplotype for SARS-CoV-2}

@@

% \paragraph{False positives}

@@

% \paragraph{Removal of selenoproteins}

@@

% \paragraph{Topology prediction of TRDD1}

@@

% \paragraph{Bacteria have a different cell membrane}

@@

% \paragraph{synonymous mutations}

@@

% \paragraph{False positives in SNPs}

@@

% \paragraph{Low number of SNPs}

@@

% \paragraph{Selection of SNPs}

@@

% We concluded that the
% epitopes that MHC-I presents are [as/not as] likely 
% to be derived from TMH within either a human host and its bacterial pathogen.
% Because a bacterium does not infect a cell, thus its peptides
% will not be presented by MHC-I, this result is [unexpected/expected]
% 
% We aimed our evolutionary experiment at TMHs, because these can
% be predicted well from a protein structure,
% are common structures and are present in all pathogens. 
% We could have done the same experiment on beta-turn,
% as also these can be predicted well (\cite{petersen2010netturnp}),
% are common structures and are present in all pathogens.
% 
% The human immune system and human pathogen are in an evolutionary
% arms race: our immune systems is selected for the detection
% of pathogens, whereas pathogens are selected to avoid detection.
% From a pathogen's point of view, however, this struggle 
% is of only minor importance:
% in seasonal influenza, for example, the selection pressure
% exerted by the immune system was only limited (\cite{han2019individual}).

@@

% \paragraph{TMH prediction software}

@@

% \paragraph{IC50 prediction software}

@@

% \paragraph{Definition of what a binder is}

@@

% \paragraph{Unclear handing of sequences with U}

@@

@@

Per target proteome (i.e. human, SARS-CoV-2, Mycobacterium tuberculosis),
we collected all 9-mers (for MHC-I) and 14-mers (for MHC-II),
after removing the selenoproteins and proteins that are shorter
than the epitope length.
From these epitopes, per MHC haplotype,
we predicted the IC50 (in nM) using \verb;epitope-prediction; (for MHC-I)
and MHCnuggets (for MHC-II). 
Here, we show the IC50 value per haplotype that
is used to determine if a peptide binds to the haplotype's MHC
for MHC-I (see table \ref{tab:ic50_binders_mhc1}) and 
MHC-II (see table \ref{tab:ic50_binders_mhc2}).

@@
